\documentclass[12pt]{article}

\begin{document}
\title{HOSTELS RESEARCH }
\author{Kyagera Sulaiman 15\u\6849\ps}
\date{May, 21, 2017}
\maketitle

\section{Introduction}
Hostels are very importants as they are the major palces of accomodation for students in different universities as well as some members of the working class in different parts of the country. Different hostels accomodate different groups and genders of people. most hostels are  mixed and accomodate both male and female students whereas other hostels are single hostels which accomodate only one gender, either male students only or female students only. But our study is going to concetrate data collection in the differents hostels.


\section{Background}
According to my research, basically I took a case study in Uganda where different hostel managers have diiferent views of how to collect information about the students they accomodate in the hostels they are managing. There are formal and informal methods but they all depend on the different views peopleostels have who manage the h have.
On the other hand, there are very many hostels in Uganda as country excluding parts of the world other .  Different hostels accomodate different students at diffent costs depending on kind of room your want to occupy, for  example double rooms and single room.

\section{Problem Statment}
This project will address the different challenges being faced by people which includefailure to pay hostel fees , loss of property while in hostels, insecurity while in hostels and misunderstanding amongstudents while in hostels and the areas surrounding the hostels.
In this section we are going to also consider the hostel problems impact on the environment.

\section{Objectives}
\subsection{Main Objective}
To look at the significances of hostels, the various types which include single hostels, mixed hostels . we will aso look at the various  challenges and effects caused due to staying in hostels.

\section{Literature review}
Here we look at  the different aspects of a good hostel. Most  ensure proper sanitation and cleanliness as well as safety of the students in the hostelsl. Hostel managers ensure that students are provided with clean water and electricity to ensure the well being and hygiene if students at the hostel. And also hostels are either mixed to accomodate both male and female students or single to accomodate either male or female students but not both.
	

\section{Methodology}
 Hostels are ususally either single hostels or mixed hostels  with the provision of accomodating only the students who pay for the hostel servieces, other students who do not reside at a particular hostel are allowed to visit their collegues  but are not allowed to sleep over as per the rules and regulations that are set up by the hostel.before one is accomodated at a given hostel he has to pay required hostel fees and also recieve a copy of the hostel rules  and regulations. 
 Students are assigned rooms which all have different keys to prevent bad behaviour like theft and robbery in the hostels.
Some hostels provide luxurious services like gym, sauner services as well as digital television to there students but it depend s on how much money u pay at a given hostel.
According to this research different data collection tools were using but mostly the Open data kit was used. Where a server for information storage was developed using the Google Cloud Platform and an Aggregate server. The open data kit build was used to formulate forms that were used in the field.

\section{References}
1. The Hostel Book. Peter Wrednapp
2. "hostels, n.". OED Online. Oxford University Press. September 2012. Retrieved 2014-09-29.

\end{document}
