\documentclass[24pt,a4paper]{article}


\begin{document}
\title{A RESEARCH ABOUT DATA COLLECTIONS IN HOSTELS.. }
\maketitle

\section{Problem: }
The best way to  collect information and hostel fees from students  who are to be accommodated in a particular hostel.

\section{Scope: }
the scope is briefly about what measures  the different hostel managers use to collect data about students as well as the most efficient ways to collect hostel fees from the students.
\section{Interview:}
So I conducted  interviews asking a few hostel managers how they collect data about students that are to be accommodated at the hostel as well as how they collect hostel fees from the accommodated students.
I also asked them the  number of students accommodated at the given hostels.

\section{Internet:}
I used the internet to create my form which I used to collect data on my android device
I  used internet access to collect data about different hostels, the data includes GPRS location coordinates,
 I also used the internet to set set up my Aggregate server where I upload and store my collected data 
 


\section{Materials required:}
The materials   I used  for my research include, a computer which I used to access the internet to create my form and Aggregate server, An android device on which I installed my ODK collect application which I used for data collection as well as internet access.

\section{Experimenting from research.}
In my research I needed to know which the best way to collect student data and  hostel fees from students  that are accommodated by different hostels and why they collect the data.

\section{Challenges: }
As any other research, challenges were faced. These included;
(i)	Some hostel managers were rude and did not cooperate very well, so I had to find information from other hostel employees who were willing to be interviewed
(ii)	some hostel managers did not  trust me with there information so they resorted  to giving me false information which nullified my researchSome people give false comments just because they don’t like the style of play of the team.
(iii)	some hostels I made research about did not collect information about students being accommodated so my research on these hostels was irrelevant.


\section{Theoretically:}
Theoretically I would prefer that  most hostels create a database for the students data as well as create a bank account on which the   students pay the hostel fees and present their bank receipts to the hostel manager when coming to the hostel for a new semester. 

\section{Conclusion.}
The more methods of hostel data collection acquire help you get to know the best way to collect student data from different hostels as well as the best way students can pay the the hostel fees.


\section{KYAGERA SULAIMAN   15/U/6849/PS   215008420}
\end{document}